\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{amsmath}
\usepackage[hmargin=3cm,vmargin=6.0cm]{geometry}
\topmargin=-2cm
\addtolength{\textheight}{6.5cm}
\addtolength{\textwidth}{2.0cm}
\setlength{\oddsidemargin}{0.0cm}
\setlength{\evensidemargin}{0.0cm}
\usepackage{indentfirst}
\usepackage{amsfonts}

\begin{document}

\section*{Student Information}

Name : Ahmet Eren Çolak\\

ID : 2587921\\

\section*{Answer 1}
\subsection*{a)}
Confidence intervals for mean of a sample with known standart deviation can be calculated as:
\begin{equation*}
	\overline{x} \pm z_{\alpha/2} \cdot \frac{\sigma}{\sqrt{n}}
\end{equation*}
Mean of sample above,$\overline{x}$ equals to $16.96$, sample size $n$ equals to $10$ and standart devation of sample $\sigma$ equals to $3$.\\
For $\%90$ confidence interval $z_{0.05} = 1.645$.

\begin{equation*}
	(16.96 - z_{0.05} \cdot \frac{\sigma}{\sqrt{n}}, \ 16.96 + z_{0.05} \cdot \frac{\sigma}{\sqrt{n}})
\end{equation*}
\begin{equation*}
	(15.38, \ 18.52)
\end{equation*}

For $\%99$ confidence interval $z_{0.005} = 2.57$.
\begin{equation*}
	(16.96 - z_{0.005} \cdot \frac{\sigma}{\sqrt{n}}, \ 16.96 + z_{0.005} \cdot \frac{\sigma}{\sqrt{n}})
\end{equation*}
\begin{equation*}
	(14.52, \ 19.40)
\end{equation*}

\subsection*{b)}
For $\%98$ confidence interval margin is $z_{0.01} \cdot \frac{\sigma}{\sqrt{n}}$ and $z_{0.01}$ equals to $2.33$.

\begin{equation*}
	z_{0.01} \cdot \frac{3}{\sqrt{n}} = 1.55
\end{equation*}
\begin{equation*}
	\sqrt{n} = 4.51
\end{equation*}
\begin{equation*}
	n = 20.34
\end{equation*}

$n$ must be at least $21$.

\section*{Answer 2}
\subsection*{a)}
No, they are not enough. Standart deviation is also required to conduct a hypothesis about a restaurant.

\subsection*{b)}
%Reject explain **
$H_0: \mu = 7.5$\\
$H_A: \mu < 7.5$\\
$\alpha = 0.05$\\
$\overline{x} = 7.4$\\
$s= 0.8$\\
$n = 256$\\

Since customer ratings are independent and identically distributed, sample mean $\overline{x}$ has a normal distribution. When null hypothesis $H_0$ is assumed to be true, $t$ value must be greater than $-t_{\alpha}$ with the degree of freedom $255$.

\begin{equation*}
	t = \frac{\overline{x} - \mu}{s / \sqrt{n}} = \frac{7.4 - 7.5}{0.8 / \sqrt{256}} = -2
\end{equation*}
\begin{equation*}
	-t_{\alpha} = -t_{0.05} = -1.645
\end{equation*}

Since $-2$ is not greater than $-1.645$, null hypothesis is rejected. Thus, this restaurant would not be in my list.
\subsection*{c)}
%Accept Explain ***
When $t$ value in previous part recalculated with $s= 1.0$:
\begin{equation*}
	t = \frac{\overline{x} - \mu}{s / \sqrt{n}} = \frac{7.4 - 7.5}{1 / \sqrt{256}} = -1.6
\end{equation*}

Since $-1.6$ is greater than $-1.645$, null hypothesis is accepted. Thus this restaurant would be in my list.
\subsection*{d)}
Since $7.6$ is greater than $7.5$, $t$ value will always be a positive number. Because of that, $t$ value will never be less than $-t_{\alpha} = -t_{0.05} = -1.645$. That is why, there is no need for a hypothesis test.

\section*{Answer 3}
\subsection*{a)}
$H_0: \mu_A - \mu_B = 90$\\
$H_A: \mu_A - \mu_B < 90$\\
$\alpha = 0.01$\\
$\overline{X}_A = 211$\\
$\overline{X}_A = 133$\\
$s_A= 5.2$\\
$s_B = 22.8$\\
$n_A = 20$\\
$n_B = 32$\\

When null hypothesis $H_0$ is assumed to be true, $t$ value must be greater than $-t_{\alpha}$ with the degree of freedom $50 \ (n_A + n_B - 2)$. The $t$ value when variances of $A$ and $B$ are assumed to be same, is:

\begin{equation*}
	t = \frac{ \overline{X}_A - \overline{X}_B - 90}{s_p \sqrt{1/n_A + 1/n_B}}
\end{equation*}

Where $s_p$, the pooled standart deviation is:

\begin{equation*}
	s_p = \sqrt{\frac{(n_A - 1)s_A^2 + (n_B - 1)s_B^2}{n_A + n_B - 2}} =  \sqrt{\frac{(19)5.2^2 + (31)22.8^2}{50}} = 18.237
\end{equation*}

Then $t$ value is:

\begin{equation*}
		t = \frac{ 211 - 133 - 90}{18.237 \sqrt{1/20 + 1/32}} = -2.308
\end{equation*}

$-t_{0.01}$ with the degree of freedom $50$ approximately equals to $-2.4$. Since $t$ value ($-2.308$) is greater than $-2.4$, null hypothesis is accepted. Researcher can claim that computer B provides a 90-minute or better performance when population variances are assumed to be same.

\subsection*{b)}
When population variances are not assumed to be same, $t$ value equals to:

\begin{equation*}
		t = \frac{ \overline{X}_A - \overline{X}_B - 90}{\sqrt{s_A^2/n_A + s_B^2/n_B}} = \frac{ 211 - 113 - 90}{\sqrt{5.2^2/20 + 22.8^2/32}} = -2.86
\end{equation*}

Degree of freedom for the $t_{\alpha}$ value is estimated by the Satterthwaite approximation:

\begin{equation*}
	\nu = \dfrac{\left (\dfrac{s_A^2}{n_A} + \dfrac{s_B^2}{n_B} \right )^2}{ \dfrac{s_A^4}{n_A^2(n_A-1)} + \dfrac{s_B^4}{n_B^2(n_B-1)} }
\end{equation*}

When all values subsituted $v$ is found to be approximately $36$. Thus $-t_{0.01}$ equals to approximately $-2.44$. Since $t$ value ($-2.86$) is not greater than $t_{0.01}$ ($-2.44$), null hypothesis is rejected. Hence researcher can not claim that computer B provides a 90-minute or better performance when population variances are not assumed to be same.
\end{document}
